\documentclass[]{resumebb}
\let\mathdollar\relax
\begin{document}
\thispagestyle{empty} % Remove page number
% Header
\namesection{Bhavya Bhatt}{38 King Street, Leicester, LE16RP}
\contactline{LinkedIn: \href{https://www.linkedin.com/in/bhavya-bhatt-5a9ab417a/}{bhavya-bhatt}}
{Email: \href{mailto:bhb6@student.le.ac.uk}{bhb6@student.le.ac.uk}}
{Phone: \href{tel:+447733380479}{(+44) 7733380479}}
{GitHub: \href{https://www.github.com/Harry-122}{Harry-122}}

\vspace{-5pt}
\hrule width \textwidth height 0.1pt

% Professional Summary
\section{\Large Profile}
\sloppy
A motivated Computer Science student with 2+ years of experience in backend development, specializing in Java, Spring Boot, and microservices. Skilled in building scalable systems, developing RESTful APIs, and optimizing database performance using Kafka, MySQL, and Elasticsearch. Proficient in designing secure and efficient solutions, with hands-on experience in AWS and distributed systems. Contributed to mission-critical applications at Amazon, Accolite Digital, and Birdeye, implementing secure, efficient, and maintainable solutions. Currently pursuing a Master’s in Advanced Computer Science at the University of Leicester, further enhancing expertise in cloud computing, cybersecurity, and software quality assurance. Passionate about competitive programming, regularly participating in various contests to refine DSA and problem-solving skills.


% Education
\section{\Large Education}
\vspace{-2pt}
\noindent
\begin{tabularx}{\textwidth}{@{}X r@{}}  
    \textbf{\uppercase{Master of Science} (MSc)} & \textsc{University of Leicester, United Kingdom} \\  
    \textit{Advanced Computer Science} & \textit{January 2024 – May 2025} \\
    \textbf{Expected:} 76\% (Distinction)\\
    [0.15cm]  

    \textbf{\uppercase{Bachelor of Technology (B.Tech.)}} & \textsc{Dhirubhai Ambani Institute (DA-IICT), India} \\  
    \textit{Information and Communication Technology (ICT)} & \textit{August 2017 – May 2021} \\  
    \textbf{Minor:} Computational Science \quad | \quad \textbf{Aggregate/CPI:} 8.12/10 \\  
\end{tabularx}


% Experience
\section{\Large Experience}
\vspace{2pt}
\runsubsection{Birdeye}
\descript{| Software Backend Engineer}
\location{September 2022 – December 2023 | Gurugram, India}
\begin{tightemize}
    \item Developed a trackable appointment form system using Java, Spring Boot, Kafka, and Apache NiFi, allowing businesses to monitor customer interactions effectively and increasing appointment conversions by 20\% through real-time engagement tracking.
    \item Built a real-time visualization dashboard with Elasticsearch, enabling peers to analyze system performance, failure metrics, and service up-time trends, leading to a 15\% reduction in downtime and improved operational insights.
    \item Optimized a high-traffic microservices architecture by integrating Kafka and Apache NiFi, processing over 100K+ daily data events, improving system scalability, and reducing end-to-end request latency by 30\%.
    \item Enhanced backend performance and efficiency by leveraging Aerospike caching, fine-tuning database queries, and optimizing API processing, enabling the system to handle 10,000+ concurrent API requests with a 99.9\% success rate.
\end{tightemize}
\sectionsep

\runsubsection{Accolite Digital}
\descript{| Software Engineer}
\location{July 2021 – September 2022 | Bengaluru, India}
\begin{tightemize}
    \item Developed and deployed an internal seat-booking web application using Spring Boot (backend) and Angular (frontend), ensuring seamless office space allocation for 500+ employees during COVID-19, improving office capacity planning.
    \item Automated data extraction and processing workflows from Gmail APIs using Java, Apache POI, and cron jobs, transforming unstructured CSV email data into detailed leadership reports, reducing manual effort by 80\%.
    \item Collaborated on full-stack development of internal tools, integrating TypeScript, RESTful APIs, and Spring Boot, reducing API response time by 30\% and increasing system reliability through enhanced backend optimizations.
    \item Enhanced internal website functionality by adding CSV export features, email distribution capabilities, and interactive UI elements, improving user productivity by 25\% and streamlining data sharing across teams.
\end{tightemize}
\sectionsep

\runsubsection{Amazon}
\descript{| Software Development Engineer Intern}
\location{January 2021 – July 2021 | Bengaluru, India}
\begin{tightemize}
    \item Designed and implemented a mobile push notification system for Amazon Pay using Java, Spring Boot, AWS Lambda, and Amazon SNS, increasing customer engagement by 15\% through timely transactional alerts.
    \item Automated AWS infrastructure setup by provisioning VPCs, hosted zones, and API gateways via backend code, eliminating 90\% of manual documentation efforts and enabling smoother cloud deployment.
    \item Integrated Amazon SQS for queuing notifications and utilized AWS Lambda for serverless computation, achieving 99.8\% message delivery reliability and ensuring seamless scalability for high-traffic workloads.
    \item Adopted Agile methodologies and Git workflows, collaborating with cross-functional teams to streamline development cycles, ensuring 100\% adherence to deadlines and delivering zero critical defects in production.
\end{tightemize}

\vspace{-4pt}
% Projects
\section{\Large Projects}
\vspace{2pt}
% \runsubsection{Distributed Whiteboard Application}
% \descript{| OpenStack}
% \location{December 2024}
% \begin{tightemize}
%     \item Designed a cloud-based distributed whiteboard application using OpenStack as part of the Internet \& Cloud Computing course.
%     \item Implemented real-time updates and conflict resolution for seamless drawing and editing across users.
% \end{tightemize}
% \sectionsep
\runsubsection{Flight Journeys System}
\descript{| Java, Agile, Software Engineering Principles}
\location{March 2024}
\begin{tightemize}
    \item Developed a robust console-based flight booking system with secure user authentication, booking management, and admin controls, ensuring 100\% data integrity and seamless transaction processing.
    \item Led an Agile-driven development cycle, executing two successful sprints using GitHub issue tracking, Planning Poker for story point estimation, PERT analysis for critical path optimization, and COCOMO-based cost estimation, achieving 90\% sprint efficiency.
    \item Designed and executed comprehensive software quality assurance tests, implementing both black-box and white-box methodologies, achieving 97\% test coverage and ensuring zero critical defects for maximum system stability.
\end{tightemize}
\sectionsep
\runsubsection{Spring Boot Application Generation Using Groovy and Xtext}
\descript{| Groovy, Xtext, EMF}
\location{December 2024}
\begin{tightemize}
    \item Engineered a Spring Boot project generator leveraging Xtext and Groovy, automating the creation of essential components such as pom.xml, application.properties, SpringBootApplication.java, entities, DTOs, repositories, services, and controllers, tailored for a Twitter-like schema (users, tweets, likes, followers).
    \item Designed a custom domain-specific language (DSL) using Xtext, enabling seamless definition of Spring Boot project models with annotations, cardinalities, and complex entity relationships (e.g., @OneToMany, @ManyToOne), alongside automated JPA repository generation.
    \item Developed a Groovy-based code generator, transforming DSL models into Spring Boot project skeletons, efficiently resolving Xtext grammar conflicts, automating REST API generation, and ensuring scalability through domain-driven design (DDD) principles.
\end{tightemize}
\sectionsep
\runsubsection{NoSQL vs SQL Query Performance Analysis}
\descript{| Groovy, MongoDB}
\location{May 2024}
\begin{tightemize}
    \item Implemented a MongoDB-based cloud solution to process and analyze Twitter data (Tweet ID, Reach, Sentiment, Location), automating the transformation of 100,000+ CSV records into structured JSON datasets and loading them into MongoDB Atlas Cloud.
    \item Optimized MongoDB query performance by indexing LocationID and Country fields, improving response time by 40\% (down to 7ms) through strategic data selection, projection, filtering, and aggregation, enabling real-time business insights.
    \item Conducted a MongoDB vs SQL performance benchmark, enhancing query execution efficiency on 10,000+ tweets, achieving a 15\% speed improvement. Demonstrated the scalability of NoSQL cloud solutions through query optimization and Agile-driven system analysis.
\end{tightemize}
\sectionsep
\runsubsection{Client-Server Application}
\descript{| Spring Boot + Java}
\location{March 2024}
\begin{tightemize}
    \item Designed and developed a highly secure client-server messaging system using Java socket programming, implementing RSA encryption (RSA/ECB/PKCS1Padding) and digital signatures (SHA256withRSA) for secure authentication and 100\% encrypted communication.
    \item Applied MD5 hashing for user identity protection, ensuring complete anonymization of stored user data, preventing unauthorized access, and guaranteeing zero plaintext message leaks, even in the event of server compromise.
    \item Engineered an optimized encryption workflow for secure message storage and relay via an intermediary server, enhancing key management, signature validation, and end-to-end security, doubling message retrieval speed for high-performance communication.
\end{tightemize}
\vspace{-3pt}

% Compact ATS-Friendly Skills & Highlights (Tabular)
% \section{\Large Skills \& Highlights}
% \vspace{-2pt}
% \begin{tabularx}{\textwidth}{@{}X X@{}}
% \textbf{Programming:} Java (Experienced), C/C++ (Proficient), Python, DSA  & \textbf{Hackathon Huawei:} Finalist (8th Position) \\
% \textbf{Backend Development:} Spring Boot, Rest APIs, Micro-services  & \textbf{CodeChef:} 2180 (5-star) \\
% \textbf{Tools:} Git, Docker, Apache NiFi, Elasticsearch, MySQL, PostgreSQL  & \textbf{Codeforces:} 1642 (Expert) \\
% \textbf{Cloud \& Platforms:} AWS (Lambda, SNS, VPC), OpenStack  & \textbf{HackerRank:} Gold Badges in C++ and problem-solving \\
% \end{tabularx}


\section{\Large Skills}
\vspace{3pt}
\textbf{Programming:} Java (Experienced), C/C++ (Proficient), Python, Groovy, Data Structures \& Algorithms (DSA) \\
\vspace{3pt}
\textbf{Backend Development:} Spring Boot, Microservices, REST APIs, Kafka, Apache NiFi \\
\vspace{3pt}
\textbf{Cloud \& Platforms:} AWS (Lambda, SQS, SNS, VPC), OpenStack, Docker, Kubernetes \\
\vspace{3pt}
\textbf{Databases:} MySQL, PostgreSQL, MongoDB, Elasticsearch, Aerospike \\
\vspace{3pt}
\textbf{Software Engineering:} Agile (Scrum \& Kanban), TDD, CI/CD, Git \\
\vspace{3pt}
\textbf{Soft skills:} Problem-Solving, Analytical, Collaboration \& Teamwork, Leadership, Communication, Adaptability \& Learning \\


\section{\Large Highlights}
\vspace{3pt}
\textbf{Huawei Hackathon 2024 (Ireland):} Finalist (8th Place) – Optimized server costs using dynamic programming \\
\vspace{3pt}
\textbf{CodeChef:} 2180 (5-star) \\
\vspace{3pt}
\textbf{Codeforces:} 1642 (Expert) \\
\vspace{3pt}
\textbf{HackerRank:} Gold Badges in C++ and problem-solving \\

\end{document}